---
title:
author:
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
#description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
github-repo: childpovertyactionlab/wic-participation-reports
favicon: "images/favicon.ico"
---

# Trust Her Webmap {-}

```{r, include = FALSE}
library(googlesheets4)
library(tidyverse)
library(sf)
library(tidycensus)
library(leaflet)
library(mapboxapi)
library(fasterize)

#Clinics
TrustHerClinic <- range_read("https://docs.google.com/spreadsheets/d/1QSeMpSoZRFPMW4l4P3k0LE_brDKARhGXrGgrkD83FsQ/edit#gid=472929183", sheet = "Clinic Sites Master") %>%
  st_as_sf(., coords = c("Longitude", "Latitude"), crs = 4326)
#DART Rail stops
DART_Rail <- st_read("C:/Users/micha/CPAL Dropbox/Data Library/DART/LightRailStations.shp") %>%
  st_transform(crs = 4326)

#DART Bus stops
DART_Bus <- st_read("C:/Users/micha/CPAL Dropbox/Data Library/DART/BusStops_2018.shp") %>%
  st_transform(crs = 4326)

#Teens Births 2018
TeenBirths <- st_read("C:/Users/micha/CPAL Dropbox/Basic Needs/04_Projects/Teen Births/Data/TeenBirths.gpkg", layer = "Teen Births") %>%
  st_transform(crs = 4326)

tb_pal <- colorBin("BuPu", domain = TeenBirths$teen_br, bins = 5)

#Drive Time
th_iso <- mb_isochrone(TrustHerClinic,
                       profile = "driving",
                       denoise = 0.25,
                       time = 1:15,
                       access_token = "pk.eyJ1IjoibWljaGFlbGNwYWwiLCJhIjoiY2tnMmI5ejgyMDFhZDJxdDNqZjV4cmJ1aiJ9.Wy-HsM9Q6hyabrmIezakbQ")

iso_pal <- colorBin("BuPu", th_iso$time, 3, na.color = "transparent")

isos_proj <- st_transform(th_iso, 32615)

template <- raster(isos_proj, resolution = 100)

iso_surface <- fasterize(isos_proj, template, field = "time", fun = "min")

#WRA
variables <- load_variables(year = 2019, dataset = "acs5/subject")

acs_var <- c(women_tot = "S0101_C05_001",
         women_15t44 = "S0101_C05_024", #total women between 15-44
         women_45t49 = "S0101_C05_011" #total women between 45-49
)

WRA <- get_acs(geography = "tract",
               state = "TX",
               county = "Dallas County",
               variables = acs_var,
               year = 2019,
               output = "wide",
               geometry = TRUE,
               ) %>%
  mutate(women_15t49 = women_15t44E+women_45t49E,
         women_per = round(women_15t49/women_totE, digits = 3)*100)  %>%
  st_transform(crs = 4326)

wra_pal <- colorBin("BuPu", domain = WRA$women_per, bins = 5)
```

Trust Her webmap for internal use only.
Webmap contains toggle selections in order to turn various datasets on or off dependent on need. 

* **Trust Her Clinics:** Locations of current Trust Her clinics based on location and clinic system.

* **Teen Births:** Teen Birth Rate per 10,000 women between 15 to 19 years old by zip code for 2018. This estimate may be skewed for certain zip codes as teen birth data is not provided by the state when there are fewer than 20(?) births per zip code by group, instead an NA value is given. Value currently in each zip code is a sum of teen births excluding any possible NA values.

* **Car Travel Time:** Raster layer visualizing the average travel time to a Trust Her clinic within a 15 minute drive time. This layer does not account for traffic and all travel times should be evaluated based on that caveat.

* **Women (15 to 49):** Census tracts layer visualizing women of reproductive age (between 15 to 49 years old) across Dallas County.

* **DART Bus:** Locations of DART bus stops across Dallas County.

* **DART Rail:** Locations of DART rail stations across Dallas County.

```{r, fig.height=7, fig.width=7, echo=FALSE, message=FALSE, warning=FALSE}
cpal_style <- "https://api.mapbox.com/styles/v1/owencpal/ckecb71jp22ct19qc1id28jku/tiles/256/{z}/{x}/{y}@2x?access_token=pk.eyJ1Ijoib3dlbmNwYWwiLCJhIjoiY2tlYnR3emdxMGNhZzMwb2EzZWR4ajloNCJ9.P7Mujz8F3Rssq5-Q6dcvMw"

map_attr <- "© <a href='https://www.mapbox.com/map-feedback/'>Mapbox</a> Basemap © <a href='https://childpovertyactionlab.org/'>Child Poverty Action Lab</a>"

leaflet() %>%
  setView(lng = -96.7970, lat = 32.7767, zoom = 10) %>%
  addTiles(urlTemplate = cpal_style, attribution = map_attr) %>%
  addRasterImage(iso_surface, 
                 colors = iso_pal, 
                 opacity = 0.6,
                 group = "Car Travel Time") %>%
  addLegend(values = th_iso$time, pal = iso_pal,
            title = "Drive Minutes to Clinic",
            position = "bottomright",
            group = "Car Travel Time") %>%
  addPolygons(data = WRA,
              color = "#525252",
              weight = 1,
              smoothFactor = 0.2, 
              fillOpacity = 0.6,
              fillColor = ~wra_pal(women_per),
              group = "Women (15 to 49)") %>%
  addPolygons(data = TeenBirths,
              stroke = TRUE,
              color = "#525252",
              weight = 1,
              smoothFactor = 0.2, 
              fillOpacity = 0.6,
              label = paste("Teen Birth Rate:", round(TeenBirths$teen_br, digits = 1), "NA Groups:", TeenBirths$births_NA),
              fillColor = ~tb_pal(teen_br),
              group = "Teen Births") %>%
  addLegend(values = TeenBirths$teen_br, pal = tb_pal,
            position = "bottomright",
            title = "Teen Births (Per 10k)",
            group = "Teen Births") %>%
  addLegend(values = WRA$women_per, pal = wra_pal,
            position = "bottomright",
            title = "Percent Women (15 to 49)",
            group = "Women (15 to 49)") %>%
  addCircleMarkers(data = TrustHerClinic,
                   stroke = FALSE,
                   radius = 6,
                   fillOpacity = 1,
                   fillColor = "#008097",
                   label = paste(TrustHerClinic$Clinic, " ", TrustHerClinic$System),
                   group = "Trust Her Clinics") %>%
  addCircleMarkers(data = DART_Rail,
                   stroke = FALSE,
                   radius = 4,
                   fillOpacity = 1,
                   fillColor = "#2f2f2f",
                   group = "DART Station") %>%
  addCircleMarkers(data = DART_Bus,
                   stroke = FALSE,
                   radius = 1,
                   fillOpacity = 1,
                   fillColor = "#2f2f2f",
                   group = "DART Bus") %>%
  addLayersControl(
    overlayGroups = c("Trust Her Clinics", "Teen Births", "Car Travel Time", "Women (15 to 49)", "DART Bus", "DART Station"),
    position = "topright",
    options = layersControlOptions(collapsed = FALSE)) %>%
  hideGroup(c("DART Bus", "DART Station", "Women (15 to 49)", "Car Travel Time"))

```